---
title: >
  The DeconvExplorer User's Guide
author:
- name: Constantin Zackl
  affiliation: 
  - Institute of Medical Biostatistics, Epidemiology and Informatics (IMBEI), Mainz
  email: zacklcon@uni-mainz.de
- name: Federico Marini
  affiliation: 
  - Institute of Medical Biostatistics, Epidemiology and Informatics (IMBEI), Mainz
  email: marinif@uni-mainz.de
date: "`r Sys.Date()`"
output: 
  bookdown::html_document2:
    toc: true
    toc_float: true
vignette: >
  %\VignetteIndexEntry{The DeconvExplorer User's Guide}
  %\VignetteEncoding{UTF-8}  
  %\VignettePackage{DeconvExplorer}
  %\VignetteKeywords{GeneExpression, RNASeq, Visualization, GUI}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
bibliography: DeconvExplorer.bib
---

<style type="text/css">
.smaller {
  font-size: 10px
}
</style>

**Package:** `r paste('DeconvExplorer', packageVersion('DeconvExplorer'))`

**Compiled date**: `r Sys.Date()`

**Last edited**: 2022-09-14

**License**: `r packageDescription("DeconvExplorer")[["License"]]`

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  error    = FALSE,
  warning  = FALSE,
  eval     = TRUE,
  message  = FALSE,
  fig.width = 10
)
options(width = 100)
```

---

# Introduction {#introduction}

This vignette describes how to use the `DeconvExplorer` package for...



In order to use `DeconvExplorer` in your workflow, the following inputs are required: 

- 



The data is made available via the ...



# Getting started {#gettingstarted}

To install this package, start R and enter:

```{r install, eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
  install.packages("BiocManager")

BiocManager::install("DeconvExplorer")
```

Once installed, the package can be loaded and attached to your current workspace as follows:

```{r loadlib, eval = TRUE}
library("DeconvExplorer")
```

If you have all four input elements ready, you can launch the `DeconvExplorer()` app by running:

```{r launchapp, eval=FALSE}
DeconvExplorer(...)
```



# Additional Information {#additionalinfo}

Bug reports can be posted ...
If you use `DeconvExplorer` for your analysis, please cite it as shown below:

```{r cite}
citation("DeconvExplorer")
```


# FAQs {#faqs}

**Q: Why is this package called `DeconvExplorer`?**

A: For obvious reasons :) 

# Session Info {- .smaller}

```{r sessioninfo}
sessionInfo()
```

# References {-}
